Exploratory Analysis Script

### 2024-04-04 code/eda-code/eda.qmd
Updated Predictor Variable table

We also wanted a summary table with the predictor information to include in our manuscript.
```{r}
# Selecting variables
selected_variables <- mydata[c("pct_upreg_sarc", "region", "wra", "pct_currentlymarried", "pct_nevermarried","rate_matdeaths", "rate_matdeaths_upreg", "rate_matdeaths_abs")]

selected_variables <- selected_variables %>% 
  arrange(region)

# Create table 
kable(selected_variables, caption = "Table Depicting Predictor Variables", booktabs = TRUE) %>%
  kable_styling(full_width = F, font_size = 10)

>>>>

We also wanted a summary table with the predictor information to include in our manuscript.
```{r}
# Selecting variables
selected_variables <- mydata[c("pct_upreg_sarc","pct_currentlymarried","pct_nevermarried","rate_matdeaths", "rate_matdeaths_upreg", "rate_matdeaths_abs","region", "wra")]

# Create table 
selected_variables %>%
  tbl_summary(
    by = region,
    label = list(wra ~ "Number of women of reproductive age, 15-49"),
    type = all_continuous() ~ "continuous2",
    statistic = list(all_continuous() ~ c("{mean}","{min}, {max}"))) %>%
modify_header(label ~ "**Predictor Variable**") %>%
modify_caption("**Table 1. Predictor Variables**") %>%
modify_spanning_header(all_stat_cols() ~ "Region")
